\textbf{EECS 340: Assignment 3}

### 2020-02-20 assignment_3/article.tex
✨ Add Question 4 response.
🐛 Bugfix on Question 4 with out_of_index pivot init.
🐛 Bugfix on Q4 to do recrusion with return to avoid output discarding.
✨ Add Question 4(b) sketch response.

\documentclass[11pt]{article}
\usepackage{setspace}
\setstretch{1}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\inlinecode}{\texttt}
\usepackage{etoolbox}
\usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{matrix,positioning,arrows.meta,arrows}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

@@

\author{Shaochen (Henry) ZHONG, \inlinecode{sxz517} \\ Yuhui ZHANG, \inlinecode{yxz2052}}
\date{Due and submitted on 02/20/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
\maketitle

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\section{Problem 4}

\begin{algorithm}
\caption{QuickMiss(C, D, start, end)}\label{QuickMiss}
    \begin{algorithmic}[1]
        \Procedure{QuickMiss}{C, D, start, end}
        % \State $l \gets m$
        % \State $p \gets n$
        \If {$p < r$}
            \State $left, q, right \gets \textsc{Partition}(C, D, start, end)$
            \If {$left < right$}
                \State $\textsc{Partition}(C, q+1, r)$
            \ElsIf {$right > left$}
                \State $\textsc{Partition}(C, p, q-1)$
            \Else
                \State \Return $D[q]$
            \EndIf
        \EndIf
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Partition(C, D, p, r)}\label{Partition}
    \begin{algorithmic}[1]
        \Procedure{Partition}{C, D, p, r}
        \State $r \gets r+1$
        \State $C[r] \gets D[\frac{p+r}{2}]$
        \State $q \gets p$
        \For {$i \gets p$ \textbf{to} $r-1$}
            \If {$\textsc{Compare-Strings}(C[i], C[r])$}
                \State $\textsc{Swap}(C[i], C[q])$
                \State $q \gets q+1$
            \EndIf
        \EndFor
        \State $\textsc{Swap}(C[q], C[r])$
        \State \Return $q$
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

>>>>

\documentclass[11pt]{article}
\usepackage{setspace}
\setstretch{1}
\usepackage{amsmath,amssymb, amsthm}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[hang, flushmargin]{footmisc}
\usepackage[colorlinks=true]{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage{footnotebackref}
\usepackage{url}
\usepackage{listings}
\usepackage[most]{tcolorbox}
\usepackage{inconsolata}
\usepackage[papersize={8.5in,11in}, margin=1in]{geometry}
\usepackage{float}
\usepackage{caption}
\usepackage{esint}
\usepackage{url}
\usepackage{enumitem}
\usepackage{subfig}
\usepackage{wasysym}
\newcommand{\ilc}{\texttt}
\usepackage{etoolbox}
\usepackage{algorithm}
% \usepackage{algorithmic}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{matrix,positioning,arrows.meta,arrows}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

@@

\author{Shaochen (Henry) ZHONG, \ilc{sxz517} \\ Yuhui ZHANG, \ilc{yxz2052}}
\date{Due and submitted on 02/20/2020 \\ EECS 340, Dr. Koyut{\"u}rk}
\maketitle

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\newpage
\section{Problem 4}

\subsubsection{(a)}

\begin{algorithm}
\caption{QuickMiss(C, D, p, r, missLeft)}\label{QuickMiss}
    \begin{algorithmic}[1]
        \Procedure{QuickMiss}{C, D, p, r, missLeft}
        \If {$p < r$}
            \State $q \gets \textsc{Partition}(C, p, r)$
            \If {$C[q] == D[q]$}
                \State \Return $\textsc{QuickMiss}(C, D, q+1, r, False)$
            \Else
                \State \Return $\textsc{QuickMiss}(C, D, p, q-1, True)$
            \EndIf
        \EndIf
        \If {$missLeft == True$}
            \State \Return $D[p]$
        \Else
            \State \Return $D[r+1]$
        \EndIf
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Partition(A, p, r)}\label{Partition}
    \begin{algorithmic}[1]
        \Procedure{Partition}{A, p, r}
        \State $q \gets p$
        \For {$i \gets p$ \textbf{to} $r$}
            \If {$\textsc{Compare-Strings}(A[i], A[r])$}
                \State $\textsc{Swap}(A[i], A[q])$ \Comment{Exchange the two elements.}
                \State $q \gets q+1$
            \EndIf
        \EndFor
        \State $\textsc{Swap}(A[q], A[r])$
        \State \Return $q$
        \EndProcedure
    \end{algorithmic}
\end{algorithm}

\subsubsection{(b)}

It is known that \textsc{QuickSort} has an average runtime of $O(n\log n)$ due to the fact that it is considered \textit{case 2} of the master theorem: as it has $n$ nodes on each level and with a depth of $\log n$, thus $O(n\log n)$. Our \textsc{QuickMiss} algorithm has a runtime of $O(n)$ due to it only calls \textsc{Partition} on either left portion or right portion to the \ilc{pivot}, but never both. Thus, on each level it will always has less than $n$ nodes, therefore forming a \textit{case 3} of the master theorem. The master theorem suggest, in \textit{case 3} the roots dominate the leaves and therefore determine the runtime of the algorithm -- as \textsc{QuickSort} has $n$ roots at the beginning, we may conclude it has a runtime of $\Theta(n)$.
